Interval Probability for Fuzzy Quantum Theories

### 2016-08-09 prob.tex
From: Tai, Yu-Tsung Sent: Tuesday, August 09, 2016 0:59 To: Hanson, Andrew J. <hansona@indiana.edu> Cc: Ortiz, Gerardo <ortizg@indiana.edu>; Amr A. Sabry (sabry@indiana.edu) <sabry@indiana.edu> Subject: RE: Yu-Tsung made changes in your shared folders (fwd)
Dear all,

I get a little bit stuck on the classical interval-valued probability measure. Recall that a quantum interval-valued probability measure $\bar{\mu}$ cannot correspond to any mixed state if there is no quantum real-valued probability measure $\mu$ such that
	$\mu(P) \in \bar{\mu}(P)$ 		(1)
for all $P$. The set of all $\mu$ satisfy

\begin{example}{[}One-qubit quantum probability measure{]} Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$
is almost the same as a quantum probability measure~$\mu_{\ket{0}}^{B}$,
we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
$\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1$. On the other hand, $\mu$
cannot be induced by any mixed state because $\mu(\proj{\ps})=\mu(\proj{0})=1$,
and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
state and $\rho=P$. \qed\end{example}

@@

\begin{example}{[}Quantum three-value interval-valued probability
measure{]} We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$, we can define
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
and $\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)$,
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

\begin{example}{[}Three-dimensional quantum three-value interval-valued
probability measure{]}\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
first notice that $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\[
\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
\]
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This equation
always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$.

>>>>

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$
is almost the same as a quantum probability measure~$\mu_{\ket{0}}^{B}$,
we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
$\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1$. On the other hand, $\mu$
cannot be induced by any mixed state because $\mu(\proj{\ps})=\mu(\proj{0})=1$,
and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
state and $\rho=P$. \qed\end{example}

@@

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$, we can define
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties $\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right)=1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)$
and $\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right)\subseteq\sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)$,
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
first notice that $\bar{\mu}\left(P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}\right)\subseteq\bar{\mu}\left(P_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(P_{2}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\[
\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)
\]
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This equation
always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$.
